### 2020-08-24 thesis/thesis.tex
[thesis] Proposed solutions chapter

\section{Duality}
    \subsection{Comodels}

@@

Another static analysis of the program.

\noindent
- TODO Describe what is data-flow analysis \\
- TODO Give example for constant folding \\
- TODO Propose analysis for coalgebraic effects. Not sure if that's not too much,
as it's not the goal of this thesis. Definitealy leave this section for later.

@@

Simplify semantics by separating coalgebraic effects into a new, restricted
construct in programming language

\noindent
TODO muuuch longer explanation of this topic

>>>>

\section{Duality}\label{sec:duality}
    \subsection{Comodels}

@@

Robust resource management could be also achieved by developing a static
analysis for checking whether resumption is called only once and that
configuration is properly passed.

Data-flow analysis may be the right tool for detecting such anomalies, however,
further work in this area is reserved for future.

@@

% Simplify semantics by separating coalgebraic effects into a new, restricted
% construct in programming language

Having observed in Section~\ref{sec:duality} that cooperations correspond to
state-passing transitions, we propose a calculus which exactly achieves this
semantic. We divide the solution into three parts, discussed below.

\subsection{State passing}

State passing can be done by embeding given coalgebraic theory in a state monad
over configurations, which in simpler words means, that for a set of coeffects
that we handle, we are going to store current configuration in a state.
Configuration is retrieved before performing a coeffect, and new configuration
is saved after one is handled. Passing of configuration does not leak to the
user, which creates a handy abstraction over operations that manage external
state.

\subsection{Linear usage}

Linear usage of resumptions is not going to be addressed by crafting operational
semantic that ensures that, as in~\cite{runners-in-action}, but rather on a
syntactic level where we verify that resumptions in cohandlers are one-shot and
tail recursive.

\subsection{Combining effects with coeffects}

Despite of the above means, algebraic effects that occur in the source code may
drop the resumption and thus finalization code is not going to be executed.
We address this issue by not allowing effects to escape the cohandler, which
means that we are not going to discard the execution of cohandler.
